\documentclass{article}
\title{User stories}

\begin{document}
\maketitle

\begin{enumerate}

\item As a student, I want to have an access to my UCL desk.

\item As a student, I want to have an access to my courses.

\item As a student, I want to check my schedule
\item I want to synchronize my schedule with ADE expert
\item I want to synchronize my schedule with google agenda
\item I want to add a task on my schedule with a place and time.
\item I want to be allowed to remove a task on my schedule.
\item I want to check the news or informations on UCL website. 

\item As a student, I want to know what is new on my moodle's courses.

\item As a student, I want to know when are the libraries open.
\item As a student, I want to know which library is the nearest.
\item I want to be able to book a book.
\item As a student, I want to have the list of all library and their schedule and location.
\item As a student, I want to have the list of all auditorium
\item I want to know how to go to a specific auditorium. (GPS)

\item As a student, I want to know where I can eat at noon time.
\item Check all possible sport
\item Check sport by day
\item Check sport by category.
\item Notification moodle on the app.

\item Information on bar. A lot of student would be interested by beer price comparative.

\item Activity on campus
\item Informations on different "cercle"
\item Informations on kots with project.
\item As a student, I would like to find easily a kot
\item As a student, I should find some cheap second hand object.

\item Information on academic restaurant, location, menu, price.

\item activity in the city (Movie, Bowling, ...)
	


\end{enumerate}


\end{document}

